Generating Simulated Data

### 2021-04-06 docs/SimData.Rmd
error on reading back in?

  saveRDS(svlenage, file.path(d.name, paste0(scenario.name, "_",
                                                       s, "agelensamp.rds")))

>>>>

  saveRDS(svlenage, file.path(d.name, paste0(scenario.name, "_",
                                                       s, "agelensamp.rds")))
# }
# 
#   # read saved sample from above
#   survs <- list.files(path=d.name, pattern = "agelensamp.rds", full.names = TRUE)
# 
#   survname <-  str_match(survs, paste0(scenario.name,"_\\s*(.*?)\\s","*agelensamp.rds"))[,2]
# 
#   agelensamp_data <- lapply(survs, readRDS)
# 
#   names(agelensamp_data) <- survname
# 
# 
# for(s in names(agelensamp_data)){
